(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 ms.tex

@@

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we employ the use of stellar models.
We first download the isochrone grids from the 2012 updated photometric
systems for the relevant bandpasses from the Dartmouth Stellar Evolution
Database \citep{Dotter08}.
We then interpolate the isochrones onto a grid uniformly spaced in
stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to
\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to
1000 pc).
In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
We then compare the expected apparent magnitudes to our observed photometry
to measure the likelihood of each grid point.
For each parameter, we then marginalize our likelihood over all other
parameters in order to estimate the value of the physical properties
for each star.

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may underpredict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

@@

This is Dan.

@@

>>>>

\newcommand{\dd}{{\ensuremath{\,\mathrm{d}}}}

@@

\subsection{Stellar Models}
To convert the observed photometric data into physical properties for each
star, we employ the use of stellar models.
We first download the isochrone grids from the 2012 updated photometric
systems for the relevant bandpasses from the Dartmouth Stellar Evolution
Database \citep{Dotter08}.
We then interpolate the isochrones onto a grid uniformly spaced in
stellar mass (from 0.20 to 2.0 \msun), metallicity (from \feh$=-1.5$ to
\feh$=+0.5$), age (from 1.0 to 14.0 Gyr), and log distance (from 10 pc to
1000 pc).
In our interpolation, we assume \afe$=0.0$ and $Y=0.2741$, the solar value.
We then compare the expected apparent magnitudes to our observed photometry
to measure the likelihood of each grid point.
For each parameter, we then marginalize our likelihood over all other
parameters in order to estimate the value of the physical properties
for each star.
\anytodo{This was done using MCMC right? Did you interpolate the
\emph{likelihood function} or the \emph{model predictions}?}

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may under-predict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

@@

To derive the physical planet parameters conditioned on the measured stellar
parameters, we used the posterior probability distribution for quantities
measured using the light curve---from \paperit---and re-weighted them using
the results of the photometric and spectroscopic analysis.
In \paperit, the authors generated MCMC samples from the posterior
probability distribution over all the physical parameters (including stellar
mass and radius, and the planet radius) using broad, un-informative priors on
the values that are not constrained by the light curve.
As described in SOME APPENDIX, these samples can be re-weighted and used to
evaluate the posterior probability of the physical parameters of the planets
conditioned on the stellar values.
This also means that the effects of different measurements of the stellar
parameters can be easily tested by applying the method described in THAT SAME
APPENDIX.

The key assumption of this method is that the likelihood function used in
\paperit\ is correct.
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

The results are given in SOME TABLE.

@@

\appendix
\section{Computing physical planet parameters}

In \paperit, the authors generated $K$ samples from the posterior probability
distribution of the physical parameters of the systems conditioned on the
light curves using broad, un-informative priors on most of the parameters.

\begin{eqnarray}
p(w\,|\,x) &=& \frac{p(w)\,p(x\,|\,w)}{p(x)} \\
&=& \frac{q(w)\,p(x\,|\,w)}{q(x)}\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)} \\
&=& q(w\,|\,x)\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)}
\end{eqnarray}

We have $K$ samples
\begin{eqnarray}
w^{(k)} &\sim& p(w\,|\,x)
\end{eqnarray}
and the point of these samples is to do integrals of the form
\begin{eqnarray}
E[f(w)] &=& \int f(w)\,p(w\,|\,x) \dd w \quad.
\end{eqnarray}
Now, if we want to update this with a new measurement $p^\prime(w)$,
